\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-23 metatheory-condensed.tex
stuff

Most notably, \TT extends MLTT with what we call \emph{linkages}
(a namesake of the construct through which \citet{zm2017} model family
polymorphism in an OO setting).
Linkages model families, so they are like tuples, but with a twist: they
support late binding.

\TT is intended as a foundational model. So unlike our user-facing plugin,
typing is structural rather than nominal, and
it supports family polymorphism by providing MLTT-style judgments that
can be used to encode core aspects of the language supported by our
plugin, rather than building them in directly.
%
For example, \TT supports the extension of inductive types through
judgments that enable the further binding of W-types~\cite{martin1984intuitionistic} in linkages.
Also unlike our plugin, \TT does not feature automations such as
the generation of propositional equalities and partial recursors,
but it is expressive enough to encode their definitions.

>>>>

Most notably, \TT extends MLTT with what we call \emph{linkages}
(a namesake of the construct through which \citet{zm2017} model family
polymorphism in an OO setting).
Linkages model families, so they are like tuples but with a twist: they
support late binding.

\TT is intended as a foundational model. So unlike our programmer-facing plugin,
typing is structural rather than nominal, and
it supports family polymorphism by providing MLTT-style typing rules that
can be used to encode core aspects of the language supported by our
plugin, rather than building them in directly.
%
For example, \TT supports the extension of inductive types through
formation rules that enable the further binding of W-types~\cite{martin1984intuitionistic} in linkages.
Also unlike our plugin, \TT does not feature automations such as
the generation of propositional equalities and partial recursors,
but it is expressive enough to encode their definitions.

%\input{selected-typing.tex}

\noindentparagraph{Syntax.}
